Order statistics and numerical optimization

### 2019-11-15 inst/order.Rmd
more discussion

Secondly, and perhaps more importantly, likelihood is not defined at a
point; likelihood is an equivalence class of functions whose domain is
possible hypotheses.  We can only compare likelihoods for two
different hypotheses [because likelihood is only defined up to a
multiplicative constant].  And in this case, the evaluate
$(1,0,\ldots,0)$ is not a hypothesis anyone would want a likelihood
for: the likelihood is not defined at that point, and does not even
have a well-defined limit there.

>>>>

Secondly, and perhaps more importantly, likelihood is not defined at a
point; likelihood is an equivalence class of functions whose domain is
possible hypotheses.  We can only compare likelihoods for two
different hypotheses [because likelihood is only defined up to a
multiplicative constant].  And for the observation considered here,
the evaluate $(1,0,\ldots,0)$ is not a hypothesis anyone would want a
likelihood for: the likelihood is not defined at that point, and does
not even have a well-defined limit there.

To some extent this is not surprising: the numerics force one to have
a strictly positive minimum value for each $p_i$ and the fillup value
$p_{10}=1-\sum p_i$.  The likelihood maximization routine tries to
maximize $p_9/p_{10}, p_8/p_9,\ldots,p_1/p_2$ simultaneously, all
subject to the unit sum constraint $\sum p_i=1$.  And of course, if
the ratio is too high then the unit sum constraint would be violated
(given that $p_{10}$ is at its minimum value).
